MSDS 7333 Case Study 06

### 2017-06-18 MSDS7333_CaseStudy06_MBaldree_BBrock_TElkins_AKelly.Rmd
Still running into issues.
Will investigate tomorrow.
Added rest of code

---
title: "MSDS 7333 Case Study 06"
author: "Matthew Baldree, Ben Brock, Tom Elkins, Austin Kelly"
date: "June 17, 2017"
output: html_notebook
---

@@

## Introduction

@@

```{r}
df = subset(offline, posX == 24 & posY == 4 & !(mac %in% remainingAP), c(signal, angle, mac))
plotDensitySignalStrength(df)
```
<font color = "red"> &uarr; Having some trouble displaying the individual graphs here. &uarr; </font>

@@

```{r}
for (ap in c("", rejectedAP, chosenAP)){
  test = onlineSummary[, !(names(onlineSummary) %in% ap)]
  train = subset(offlineSummary, mac != ap)
  err = predictionErrors(test, train, numberOfAnglers = 1, k = 3)
  print(paste(ap, err))
}
```

```{r}
#Iterate through 1 to 3 neighbors with 1 to 3 angles for each scenario to determine best combination
#for cross validation
for (ap in c("None", rejectedAP, chosenAP)){
  if (ap == "None"){
    test = onlineSummary
    train = offlineSummary
  } else {
    test = onlineSummary[, !(names(onlineSummary) %in% ap)]
  }

  estXY = predXY(newSignals = test[, 6:11],
                 newAngles = test[, 4],
                 train, 
                 numAngles = 3, k = 3)
  actXY = test[, c("posX", "posY")]
  err = calcError(estXY, actXY)

@@

* *Which MAC address yields the best prediction of location?including determining locations by using data corresponding to both MAC addresses*
* *Does using data for both MAC addresses simultaneously yield more, or less accurate prediction of location?*

### Part 2

@@

### Preliminary Functions to be used: 
## Let's break this section up and explain each function individually

## The Output Achieved (this should be included as close as possible to the output or figures as possible)
Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

>>>>

---
title: "MSDS 7333 Case Study 06"
author: "Matthew Baldree, Ben Brock, Tom Elkins, Austin Kelly"
date: "June 17, 2017"
output:
  html_notebook: default
  html_document: default
---

@@

## Introduction
(insert text here)

@@

```{r}

```

```{r}
df = subset(offline, posX == 24 & posY == 4 & !(mac %in% remainingAP), c(signal, angle, mac))
plotDensitySignalStrength(df)
```
<font color = "red"> <b> &uarr; having issues with this diplaying properly... &uarr;</b> </font>

@@

```{r}
source("MSDS7333-baldree-case6-fx.r", print.eval = TRUE)
```

```{r}
#Iterate through 1 to 3 neighbors with 1 to 3 angles for each scenario to determine best combination
#for cross validation
for (ap in c("None", rejectedAP, chosenAP)){
  if (ap == "None"){
    test = onlineSummary
    train = offlineSummary
    newSignals = test[ , 6:12]
  } else {
    test = onlineSummary[, !(names(onlineSummary) %in% ap)]
    train = subset(offlineSummary, mac != ap)
    newSignals = test[,6:11]
  }

  estXY = predXY(newSignals = newSignals,
                 newAngles = test[, 4],
                 train, 
                 numAngles = 3, k = 3)
  actXY = test[ , c("posX", "posY")]
  err = calcError(estXY, actXY)

@@

Perform cross validation and plot for desired AP for a range of k's for each fold. We want to find k-NN estimates from 1...k and aggregate errors over the v folds.

Choose a v-fold of 11
```{r}
v = 11
```

```{r}

# number of locations
permuteLocs = sample(unique(offlineSummary$posXY))

```

```{r}
# matrix locations into folds
permuteLocs = matrix(permuteLocs, ncol = v, nrow = floor(length(permuteLocs)/v))
```
<font color = "Red"><b>&uarr; come back to this one &uarr;</b></font>

```{r}
# summarize and format offline
keepVars = c("posXY", "posX", "posY", "orientation", "angle")
onlineCVSummary = reshapeSS(offline, keepVars = keepVars, sampleAngle = TRUE)
```

```{r}
# number of k's
K = 10
# errors array
err = rep(0, K)

# loop through folds
for (j in 1:v) {
  testFold = subset(onlineCVSummary, posXY %in% permuteLocs[ , j])
  trainFold = subset(offlineSummary, posXY %in% permuteLocs[ , -j])
  actFold = testFold[ , c("posX", "posY")]

  # loop through neighbors
  for (k in 1:K) {
    estFold = predXY(newSignals = testFold[ , 6:12],
                     newAngles = testFold[ , 4],
                     trainFold, numAngles = 3, k = k)
    err[k] = err[k] + calcError(estFold, actFold)
  }
}
# plot k to sum of squared errors
plotSSErrors(err, K)
```

```{r}
# experiment with a few k's based on above analysis to determine k
# that results in lowest sum squared error on test data.
estXY = predXY(newSignals = onlineSummary[ , 6:12],
               newAngles = onlineSummary[ , 4],
               offlineSummary, numAngles = 3, k = 5)
actXY = onlineSummary[ , c("posX", "posY")]
calcError(estXY, actXY)
```

*** 
#Part 2: Alternatvie k-nearest neighbors
```{r}
# create weights for neighbors based on signal strength and multiple times X and Y and sum neighbors
# to get X and Y.
estXY = predXY(newSignals = onlineSummary[ , 6:12],
               newAngles = onlineSummary[ , 4],
               offlineSummary, numAngles = 3, k = 5, weighted=TRUE)
actXY = onlineSummary[ , c("posX", "posY")]
calcError(estXY, actXY)
```

@@
